---
title: "Reproducible reporting"
page-navigation: false
format:
  html: 
    toc: false
---

```{r, echo = FALSE, include = FALSE}
source(here::here("R", "buttons.R"))
```

Welcome to the Reproducible reporting module. This module consists of a series of *tutorials* on the following topics:

::: {.callout-tip}
## ⏱ Estimated Time to Complete
About 100–130 minutes, including practice exercises and knowledge quizzes.
:::

1.  [Quarto and markdown](/tutorials/quarto_markdown/index.qmd)
2.  [Chunks and options](/tutorials/chunk_options/index.qmd)
3.  [Writing text](/tutorials/writing_text/index.qmd)
4.  [Presenting output](/tutorials/presenting_output/index.qmd)

## Learning Goals

After completing this module, you will be able to:

### Quarto and markdown

1.  Understand the purpose of Markdown and Quarto.
2.  Understand the differences between Markdown and Quarto.
3.  Create documents and presentations with Quarto, and keep rendered files self-contained.

### Chunks and options

1.  Understand what code chunks are.
2.  Learn how to create and label R code chunks.
3.  Explore common chunk options.

### Writing text

1.  Learn how to write plain text and basic Markdown formatting to style text.
2.  Learn how to apply structure to a document.
3.  Learn how to include inline code and results within text.

### Presenting output

1.  Learn how to display clean, readable tables.
2.  Understand how to include plots and visualizations.

Click the button below to get started with the first tutorial.

```{r}
#| echo: false
#| results: asis
begin_button("/tutorials/quarto_markdown/index.html")
```
