---
title: "Reproducible reporting"
page-navigation: false
format:
  html: 
    toc: false
---

```{r, echo = FALSE, include = FALSE}
source(here::here("R", "buttons.R"))
```

Welcome to the Reproducible reporting module. This module consists of a series of *tutorials* on the following topics:

1.  [Quarto and markdown](/tutorials/quarto_markdown/index.qmd)
2.  [Chunks and options](/tutorials/chunk_options/index.qmd)
3.  [Writing text](/tutorials/writing_text/index.qmd)
4.  [Presenting output](/tutorials/presenting_output/index.qmd)
5.  [Portability and reproducibility](/tutorials/reproducibility/index.qmd)

## Learning Goals

After completing this module, you will be able to:

### Quarto and markdown

1.  Understand the purpose of Markdown and Quarto.
2.  Understand the differences between Markdown and Quarto.
3.  Recognize the different documents that can be created with Quarto.

### Chunks and options

1.  Understand what code chuncks are.
2.  Learn how to create and label R code chunks.
3.  Explore common chunk options.

### Writing text

1.  Learn how to write plain text and basic Markdown formatting to style text.
2.  Learn how to apply structure to a document.
3.  Learn how to include inline code and results within text.

### Presenting output

1.  Learn how to display clean, readable tables.
2.  Understand how to include plots and visualizations.

Click the button below to get started with the first tutorial.

```{r}
#| echo: false
#| results: asis
begin_button("/tutorials/quarto_markdown/index.html")
```
