---
title: "Tables"
---


Tables are a common way to summarize data in reports. Quarto allows you to produce tables **directly in Markdown** or **dynamically from R**. Using clear, readable tables improves the presentation of results and makes your documents more professional and accessible.

## Text-Based Tables in Markdown

For simple tables, you can write them directly in Markdown using the pipe (`|`) syntax. This is ideal for small, static tables that do not require dynamic calculations.

**Example:**

```markdown
| Group | Mean | SD  |
|-------|------|-----|
| A     | 5.2  | 1.1 |
| B     | 6.8  | 0.9 |
| C     | 4.9  | 1.3 |
```

Rendered output:

| Group | Mean | SD  |
| ----- | ---- | --- |
| A     | 5.2  | 1.1 |
| B     | 6.8  | 0.9 |
| C     | 4.9  | 1.3 |

* Use `---` under headers for proper alignment.
* Columns can be aligned left (`:` on left), right (`:` on right), or center (`:` on both sides):

```markdown
| Group | Mean | SD  |
|:------|----:|:---:|
| A     | 5.2 | 1.1 |
| B     | 6.8 | 0.9 |
| C     | 4.9 | 1.3 |
```
Results in aligned columns like this: 

| Group | Mean | SD  |
|:------|----:|:---:|
| A     | 5.2 | 1.1 |
| B     | 6.8 | 0.9 |
| C     | 4.9 | 1.3 |


## Generating Tables from R with `knitr::kable`

For tables that come from your R data (e.g., data frames, summaries), Quarto integrates seamlessly with `knitr::kable` to produce clean, nicely formatted tables.

**Example:**

When producing tables are raw output, they will look like this:
```{r}
#| echo: TRUE

library(knitr)

data <- data.frame(
  Group = c("A", "B", "C"),
  Mean  = c(5.2, 6.8, 4.9),
  SD    = c(1.1, 0.9, 1.3)
)

data
```

When using kable, they can be formatted more neatly: 
```{r}
#| echo: TRUE

kable(data, caption = "Summary statistics by group")
```


* `caption` adds a descriptive label for the table.
* `kable` automatically aligns columns neatly.
* For larger or more complex tables, you can also use **`kableExtra`** to add styling, colors, or column formatting.

```{r}
#| echo: TRUE

library(kableExtra)

mean_score <- mean(data$Mean)

kable(data, caption = paste("Summary statistics (overall mean:", round(mean_score, 2), ")")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  row_spec(0, bold = TRUE, color = "white", background = "#4CAF50")  # header row styling
```

* `kable_styling()`: Adds table styling options like **striped rows**, **hover effect**, and **condensed spacing**.
* `row_spec(0, ...)`: Styles the header row (0 = header) with **bold text**, **white font**, and a **green background**.
* The caption dynamically includes the **overall mean** calculated from the data.

Rendered in HTML, this produces a **professional, readable table** that’s visually distinct and easier to interpret than a plain `kable()` table.

You can also add row colors, column formatting, or footnotes with other `kableExtra` functions for even more control.


## Tips for Readable Tables

1. **Keep them concise**: Avoid overcrowding a table with too many columns or unnecessary decimals.
2. **Label clearly**: Use meaningful headers and, if needed, a descriptive caption.
3. **Round numbers**: Format numeric results for readability.
4. **Consistent styling**: For longer reports, stick with a single table style (Markdown or `kable`) for consistency.


::: {.column-margin}

:::: resource
For more detail, see [the Quarto documentation](https://quarto.org/docs/authoring/tables.html)
::::

:::

