---
title: "Tables"
---

Tables are a common way to summarize data in reports. Quarto can produce tables **directly in Markdown** or
**dynamically from R**. Clear, readable tables make your documents more professional and easier to follow.

## Text-Based Tables in Markdown

For small, static tables, you can write them directly in Markdown using pipe (`|`) syntax:

```markdown
| Group | Mean | SD  |
|:------|-----:|:---:|
| A     | 5.2  | 1.1 |
| B     | 6.8  | 0.9 |
```

| Group | Mean | SD  |
|:------|-----:|:---:|
| A     | 5.2  | 1.1 |
| B     | 6.8  | 0.9 |

A `---` row under the headers is required; colons control column alignment (left, right, or center).

## Generating Tables from R with `kable()`

For tables built from your own data, `knitr::kable()` produces a clean, nicely formatted table.

**Do:** Run the code below in your own Quarto document.

```{r}
data <- data.frame(
  Group = c("A", "B", "C"),
  Mean  = c(5.2, 6.8, 4.9),
  SD    = c(1.1, 0.9, 1.3)
)

data
```

**See:** The table gets printed as a raw R object, the data frame's default output isn't well suited for a report.

**Predict:** before looking below, predict how wrapping this same data frame in `knitr::kable()` will change its
appearance in the rendered document.

```{r}
library(knitr)
kable(data, caption = "Summary statistics by group")
```

**Explain:** as predicted, `kable()` renders the data as a properly formatted table matching the surrounding document
style, with a caption added via the `caption` argument, rather than R's plain console-style printout.

For more control, such as striped rows, colored headers, and similar styling, the **`kableExtra`** package extends `kable()`
output:

```{r}
library(kableExtra)

kable(data, caption = "Summary statistics by group") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) |>
  row_spec(0, bold = TRUE, color = "white", background = "#4CAF50")
```

::: {.column-margin}
::: resource
[Quarto documentation on tables](https://quarto.org/docs/authoring/tables.html)
:::
:::

::: practice

## Practice Exercise

Create a data frame with two columns of your choice (at least 3 rows), then use `kable()` to display it with a caption.

:::: {.panel-tabset}
## {{< var tab_title.editor >}}

```{webr-r}

```

## {{< var tab_title.solution >}}

```{r}
library(knitr)

scores <- data.frame(
  Student = c("Alex", "Jordan", "Sam"),
  Score   = c(88, 92, 79)
)

kable(scores, caption = "Exam scores")
```

::::

:::
