---
title: "Example presentation"
author: "Open Statistical Programming"
date: "2025-01-01"
format: 
  revealjs:
    theme: simple
    transition: slide
    code-overflow: wrap
    slide-number: true
execute:
  echo: true
  warning: false
---

# Introduction

Welcome to this short **Reveal.js presentation** created with Quarto.

This presentation demonstrates how to combine **text**, **R code**, and **visualizations** into reproducible slides.

---

## About the Data

We’ll use the built-in `mtcars` dataset to explore the relationship between horsepower (`hp`) and fuel efficiency (`mpg`).

```{r}
head(mtcars)
```

---

## Visualizing the Relationship

```{r}
library(ggplot2)

ggplot(mtcars, aes(x = hp, y = mpg)) +
  geom_point(color = "steelblue", size = 3) +
  geom_smooth(method = "lm", se = FALSE, color = "darkorange") +
  labs(title = "Fuel Efficiency vs Horsepower",
       x = "Horsepower (hp)",
       y = "Miles per Gallon (mpg)")
```

---

## Interpretation

* Cars with higher horsepower generally have **lower fuel efficiency**.
* The trend line shows a clear negative correlation between the two variables.
* Such visualizations can support discussions in reports and presentations.

---

## Summary

* **Markdown** provides the structure and narrative.
* **R** executes the analysis and visualization.
* **Quarto** integrates both to produce polished slides.

Learn more:
[Reveal.js Presentations in Quarto](https://quarto.org/docs/presentations/revealjs/)






