---
title: "Inline code and results"
---

Inline code lets you execute an R expression directly within your narrative text, so a report always reflects the
current data or computation, without manually copying results in.

## Syntax for Inline Code

Inline code is written with a single pair of backticks, starting with the language identifier:

**Do:** Run this code inline where you are writing text in your own Quarto document.

```{r}
#| eval: false
`r 2 + 2`
```

**See:** including this in a sentence runs the code and prints only the result: `r 2 + 2`.

**Predict:** now suppose a previous chunk already created an object, `mean_score <- mean(c(5, 10, 15))`. Before looking
below, predict what the following inline code will show once rendered: the code itself, or the number it evaluates to?

```{r}
#| eval: false
`r mean_score`
```

```{r}
#| include: false
mean_score <- mean(c(5, 10, 15))
```

**Explain:** as predicted, only the result appears: "The average score is `r mean_score`." The expression is evaluated
at render time, and only its result is shown; you can use any valid R expression, including objects created in earlier
chunks.

## Using Inline Code in Text

Inline code works well for numbers that should always match the current analysis. For example, the syntax

```{r}
#| eval: false
The mean mpg is `r round(mean(mtcars$mpg), 1)`.
```

renders as: The mean mpg is `r round(mean(mtcars$mpg), 1)`. The same approach works for model results:

```{r}
#| eval: false
The regression slope is `r round(coef(lm(mpg ~ wt, data = mtcars))[2], 2)`.
```

renders as: The regression slope is `r round(coef(lm(mpg ~ wt, data = mtcars))[2], 2)`.

::: {.callout-note}
## Common Mistake

Raw inline results are often much longer or messier than you'd want in a sentence: an unrounded slope like
`-5.344471517...` looks out of place in a report. Always round (`round()`) or format (`format()`) numeric results
before embedding them, rather than leaving the raw computed value to print as-is.
:::

::: practice

## Practice Exercise

Create a numeric vector called `scores` with a few values of your choice, then compute its mean rounded to 1 decimal
place, the way you would for an inline result.

:::: {.panel-tabset}
## {{< var tab_title.editor >}}

```{webr-r}

```

## {{< var tab_title.solution >}}

```{r}
scores <- c(72.456, 88.219, 91.038, 65.774)
round(mean(scores), 1)
```

If this were an inline expression in a report, e.g.

```{r}
#| eval: false
The average score is `r round(mean(scores), 1)`.
```

it would render as: "The average score is 79.4." Rounding keeps the embedded result readable in a sentence, rather than
printing several unnecessary decimal places.

::::

:::
